\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{url}
\usepackage{csquotes}
\usepackage[backend=biber,sorting=ydnt]{biblatex}

\name{Devin}{Torres}
\title{Full-Stack Engineering Lead}
\phone[mobile]{+1-512-312-8954}
\email{d@devinus.io}
\homepage{devinus.io}
\social[github]{devinus}
\social[linkedin]{devinus}
\social[twitter]{devinus}

\begin{filecontents}{resume.bib}
  @article{salesforce-acquisition,
    author  = {Ingrid Lunden},
    title   = {
  Salesforce acquires Rebel, maker of 'interactive' email services, to expand its Marketing Cloud},
    journal = "TechCrunch",
    date    = {2018-10-05},
    url     = "https://techcrunch.com/2018/10/05/salesforce-acquires-rebel-maker-of-interactive-email-services-to-expand-its-marketing-cloud/"
  }

  @article{rebel-api,
    author  = {Anthony Ha},
    title   = {
      Rebelmail launches an API to bring more interactivity to emails},
    journal = "TechCrunch",
    date    = {2016-11-15},
    url     = "https://techcrunch.com/2016/11/15/rebelmail-api/"
  }
\end{filecontents}
\addbibresource{resume.bib}

\begin{document}
\makecvtitle

\section{Experience}
\cventry{2018--Present}{Principal Member of Technical Staff}{Salesforce}{New York City}{NY}{Joined as part of the Salesforce acquisition of Rebel. \cite{salesforce-acquisition}}%
\cventry{2017--2018}{Core Team}{Nano Foundation}{Austin}{TX}{Developer as part of the Core Team for \href{https://nano.org}{Nano} -- an instant, feeless cryptocurrency.}%
\cventry{2015--2018}{Director of Engineering}{Rebel}{New York City}{NY}{As the third employee, developed the world's first and only platform to build and send interactive emails.%
  \begin{itemize}%
    \item Comprehensive REST API including several ESP, CRM, and analytics provider integrations \cite{rebel-api};
    \item Email builder using composable interactive Rebel components;
    \item Realtime analytics and reporting engine;
    \item All of this accomplished using a continuously deployed, automatically scaled microservices architecture.
  \end{itemize}}
\cventry{2014--2015}{Lead Developer}{Clutch Analytics}{Austin}{TX}{Formed and lead a new team within an aggressive timeline to develop and launch new B2B2C software solutions for the auto insurance industry.%
  \begin{itemize}%
    \item Developed a white-labeled eCommerce solution for independent insurance agents and launched before a strict deadline while under budget.
    \item Designed a highly parallelizable, next-generation insurance rater for a new market using a custom rules engine that had to conform to strict legal requirements.
    \item Managed multiple outsourced teams that augmented local teams to help deliver objectives.
  \end{itemize}}
\cventry{2007--2014}{Senior Application Developer}{Interline Vacations}{Austin}{TX}{Key member of the software design team. Responsible for several business-critical applications and websites.%
  \begin{itemize}%
    \item Maintained massive legacy codebases for in-house reservation, inventory management and CRM applications.
    \item Developed an online travel and tourism metasearch engine focusing on speed and extensibility.
    \item Redesigned and launched several multi-branded international websites.
  \end{itemize}}
\cventry{2007--2007}{VP of Internet Design}{Wythagy}{Austin}{TX}{Second in charge overseeing all technical aspects of the startup. Worked with several clients to create innovative web 2.0 applications.}
\cventry{2006--2007}{Online Creative Director}{Study Breaks Magazine}{Austin}{TX}{Responsible for all online strategies to further the magazine's web presence.}

\section{Technologies}
\cvdoubleitem{Languages}{JavaScript, TypeScript, Elixir, Erlang, Python, Rust, Go, C, C++, Shell, PHP}{Databases}{PostgreSQL, MongoDB, InfluxDB, Redis, Couchbase}
\cvdoubleitem{Frameworks}{Node.js, Ember.js, React, Electron, Phoenix}{Platforms}{Amazon Web Services, Docker, Kubernetes, Linux}

\clearpage

\section{Projects}
\cvitem{\href{https://nanowalletcompany.com/}{Nano Wallet}}{An \href{https://electronjs.org/}{Electron} desktop wallet application for the \href{https://nano.org}{Nano} cryptocurrency. \url{https://github.com/nano-wallet-company/nano-wallet-desktop}}
\cvitem{\href{https://hexdocs.pm/poison/Poison.html}{Poison}}{An \href{https://tools.ietf.org/html/rfc7159}{RFC 7159} and \href{https://www.ecma-international.org/publications/standards/Ecma-404.htm}{ECMA 404} compliant \href{http://www.json.org/}{JSON} library for \href{https://elixir-lang.org/}{Elixir} used by \href{http://phoenixframework.org/}{Phoenix}. Currently the most popular library in the \href{https://hex.pm/}{Elixir ecosystem}. \url{https://github.com/devinus/poison}}
\cvitem{\href{https://github.com/devinus/poolboy}{Poolboy}}{An \href{https://www.erlang.org/}{Erlang} worker pool implementation used by \href{http://basho.com/}{Basho} in \href{http://basho.com/products/riak-kv/}{Riak}, \href{https://www.2600hz.com/}{2600hz} in \href{https://github.com/2600hz/kazoo}{Kazoo}, \href{https://www.irccloud.com/}{IRCCloud}, \href{http://chicagoboss.org/}{Chicago Boss}, and other high profile projects. \url{https://github.com/devinus/poolboy}}

\printbibliography

\end{document}
